Probabilistic Forecasts in Hierarchical~Time~Series

### 2018-07-07 ProbabilisticCoherence.tex
Improved wording for abstract and intro

\theoremstyle{theo}
\newtheorem{theo}{Theorem}[section]

@@

\begin{abstract}
  Adjusting forecasts to ensure coherence with aggregation constraints that hold for real data - a process known as forecast reconiliation - is extended from point forecasts to probabilistic forecasts.  This is achieved by redefining forecast reconciliation in terms of linear mappings in general, and projections more specifically.  New theorems establish that the true predictive distribution can be recovered in the elliptical case by a linear mapping and general conditions are derived for when this linear mapping is a projection. A geometric interpretation is also used to prove two new theoretical results for point forecasting; that  reconciliation via projection a) preserves unbiasedness and b) dominates unreconciled forecasts in a mean squared error sense.  Strategies for forecast evaluation based on scoring rules are discussed and it is shown that the popular log score is an improper scoring rule with respect to the class of unreconciled forecasts when the true predictive disstribution coheres with aggregation constraints.  Finally evidence from simulation study show that reconciliation based on an oblique projection, derived from the MinT method of \cite{Wickramasuriya2017} for point forecasting, outperforms both reconciled and unreconciled alternatives.
\end{abstract}

%
\section{Introduction}\label{sec:intro}
%Sketch narrative to tell
%\begin{itemize}
%	\item Coherence is important in point forecasting to
%	\begin{itemize}
%		\item Align decisions
%		\item Improve forecasts
%	\end{itemize}
%	\item We propose a geometric interpretation via linear transformations including special case of projections.
%	\item These nest existing methods but the interpretation has advantages 
%	\begin{itemize}
%		\item Prove that projections preserve unbiasedness.  Previously assumed in special cases.
%		\item Prove reconciliation (using projection) always improves sum of squared errors (or a scaled/transformed version thereof).
%		\item Most importantly generalises to probabilistic forecasting.
%	\end{itemize}
%    \item For elliptical distributions, true predictive can be recovered via linear reconciliation and in special cases, via projection.
%    \item Discuss evaluation of forecasts
%    \begin{itemize}
%    	\item Log score improper when coherent v incoherent
%    	\item Energy score cn be used instead
%    	\item Discuss scores for coherent v coherent.
%    \end{itemize}
%    \item Finally evidence MinT is best from simulation
%\end{itemize}

Large collections of time series often follow some aggregation structure.  For example, the electricity demand of a country can be disaggregated according to a geographical hierarchy of states, cities, and individual households or by a temporal hierarchy of yearly, quarterly and monthly demand. In these so-called hierarchical time series, forecasts are often required for all individual series.  To ensure aligned decision making it is important for forecasts at the most disaggregated - or bottom-level - to add up to forecasts at more aggregated - or higher - levels. This property is referred to as ``coherence''.  This issue has been extensively covered for point forecasting in a literature we review below, while the case of probabilistic forecasting is a gap that we seek to address in this work.

Traditional approaches to ensure coherent point forecasts produce first-stage forecasts at a single level.  To describe these we use the small hierarchy in Figure~\ref{fig1} where the variable labelled $Tot$ is the sum of the series $A$
and series $B$, the series $A$ is the sum of series $AA$ and series $AB$ and the series $B$ is the sum of the series $BA$ and $BB$.  In the bottom-up approach \citep{Dunn1976}, forecasts are produced at the most disaggregated level (Series $AA$, $AB$, $BA$ and $BB$) and then summed to recover all top level-series.  Alternatively, in the top-down approach \citep{Gross1990} a top-level forecast is first produced (Series $Tot$) and bottom level forecasts are recovered as  historical or forecasted proportions of the top-level forecast. A middle-out approach is a hybrid between these two that for the hierarchy below would produce first stage forecasts for Series $A$ and $B$.

@@

In recent years, reconciliation methods introduced by \citet{Hyndman2011} have become increasingly popular.  For these methods, first stage forecasts are independently produced for all series rather than series at a single level.  Since these so-called `base' forecasts are rarely coherent in practice,  they are subsequently adjusted  or `reconciled' to ensure coherence.  To  date reconciliation has typically been formulated as a regression problem with alternative reconciliation methods resembling different least squares estimators. These include Ordinary Least Squares {OLS} \cite{Hyndman2011}, Weighted Least Squares {WLS} \citep{AthEtAl2017} and a Generalised Least Squares (GLS) estimator \citep{Wickramasuriya2017}, more commonly referred to as MinT since it minimises the trace of  the squared error matrix. These methods have been shown to outperform traditional alternatives across a range of simulated and real-world datasets \citep{Hyndman2011,VanErven2015a,Wickramasuriya2017} since they use information at all levels of the hierarchy and in some sense hedge against the risk of model misspecification at a single level.

A shortcoming of the existing literature is a focus on point forecasting despite an increased understanding over the past decade of the importance of providing a full predictive distribution for forecast uncertainty \cite[see][and references therein]{Gneiting2014}.  Indeed to the best of our knowledge, the as yet unpublished work of \cite{BenTaieb2017} is the only paper to deal with the issue of coherent probabilistic forecasts, and although the means of the predictive distributions are reconciled, the overall distributions are constructed in a bottom up fashion.  In contrast, the main objective of our paper is to generalise both coherence and reconciliation from point to probabilistic forecasting.

To facilitate the extension of point forecast reconciliation to probabilistic forecasting, we  first provide a geometric interpretation of existing point reconciliation methods, framing them in terms of projections.  In addition to being highly intuitive, this allows us to establish a number of theoretical results.  We prove two new theorems about point forecast reconciliation, the first showing that reconciliation via projections preserves the unbiasedness of base forecasts while the second shows that reconciled forecasts dominate unreconciled forecasts since projections are bounded operators.  We provide definitions of coherence and forecast reconciliation in the probabilistic setting and describe how these definitions lead to a reconciliation procedure that merely involves a change of basis and marginalisation.  We show that probabilistic reconciliation via linear transformations can recover the true predictive distribution as long as the latter is in the elliptical class.  We provide conditions for which this linear transformation is a projection, and although this projection cannot be feasibly estimated in practice, we provide a heuristic argument in favour of MinT reconciliation.

We also cover the issue of forecast evaluation of probabilistic forecasts via scoring rules.  In particular we prove that for a coherent data generating process, the log score is not proper with respect to incoherent forecasts.  As such we recommend the use of the energy score and variogram score for comparing reconciled to unreconciled forecasts.  Two or more reconciled forecasts can be compared using log score, energy score or variogram score, although we show that comparisons should be  made on the full hierarchy for the latter two scores.

The remainder of the papers is  structured as follows.  In section \ref{sec:definitions} coherence is defined geometrically for both point and probabilistic forecasts.  Section~\ref{sec:reconciliation} contains definitions of point and probabilistic forecast reconciliation as well as our main theoretical results.  In Section~\ref{sec:evaluation} we consider the evaluation of probabilistic hierarchical forecasts via scoring rules while a simulation study comparing unreconciled probabilistic forecasts and different kinds of reconciled probabilistic forecasts is provided in Section~\ref{sec:gaussian} and Section~\ref{sec:conclusions} concludes.

@@

%As an alternative to these traditional methods, \citet{Hyndman2011} proposed to utilize the information from all levels of the hierarchy to obtain coherent point forecasts in  a two stage process. In the first stage, the forecasts of all series are independently obtained by fitting univariate models for individual series in the hierarchy. It is very unlikely that these forecasts are coherent. Thus in the second stage, these forecasts are optimally combined through a regression model to obtain coherent forecasts. This second step is referred to as ``reconciliation'' since it takes a set of incoherent forecasts and revises them to be coherent. The approach was further improved by \citet{Wickramasuriya2017} who proposed the ``MinT'' algorithm to obtain optimally reconciled point forecasts by minimizing the mean squared coherent forecast errors.

@@

%\section{Hierarchical Time Series}\label{sec:notation}
\section{Coherent forecasts}\label{sec:definitions}
\subsection{Notation and Preliminaries}\label{sec:notation}

Throughout the paper, we will follow notational conventions used in \citet{Wickramasuriya2017} as much as possible.  A {\em hierarchical time series} is a collection of $n$ variables where some variables are aggregates of other variables and we let $\bm{y}_t \in \mathbb{R}^n$ be a vector comprised of observations of all variables in the hierarchy at time $t$. For example for the hierarchy in Figure~\ref{fig1}, $n=7$ and $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$.  The {\em bottom level series} are defined as those $m$ variables that cannot be formed as aggregates of other variables, we let $\bm{b}_t \in \mathbb{R}^m$ be a vector comprised of observations of all bottom-level series at time $t$.  For example for the hierarchy in Figure~\ref{fig1}, $m=4$ and $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$.  The hierarchical structure of the data imply the following holds for all $t$
\begin{equation}
  \bm{y}_t = \bm{Sb}_t,
\end{equation}
where $\bm{S}$ is an $n \times m$ constant matrix that encodes the aggregation constraints.  For the hierarchy in Figure~\ref{fig1}
$$ 
  \bm{S} = \begin{pmatrix} 
               1& 1 &1 &1  \\ 
               1 &1 & 0 &0 \\   
               0&0  & 1 & 1 \\ 
               & \multicolumn{2}{c}{\bm{I}_4} &   
           \end{pmatrix}, 
$$

where $\bm{I}_4$ is a $4\times 4$ identity matrix.

@@

  Let $\hat{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be any set of incoherent point forecasts at time $t+h$ using information up to and including time $t$.  Let $\bm{G}$ and $\bm{d}$ be an $m\times n$ matrix and $m\times 1$ vector respectively and $g:\mathbb{R}^n \rightarrow \mathbb{R}^m$ be the mapping $g(\bm{y})={\bm G}{\bm y}+{\bm d}$.
  \begin{definition}\label{def:reconpoint}
  The point forecast $\tilde{\bm{y}}_{t+h|t}$ ``reconciles'' $\hat{\bm{y}}_{t+h|t}$ with respect to the mapping $g(.)$ iff
  \begin{equation}
    \tilde{\bm{y}}_{t+h|t}=\bm{S}\left(\bm{G}\hat{\bm{y}}_{t+h|t}+{\bm d}\right)\,.
  \end{equation}

\end{definition}

@@

\begin{table}[!h]
	\caption{Summary of reconciliation methods that are projections. Here, $\bm{\hat{W}}^{sam}$ is the variance covariance matrix of one-step ahead forecast errors, while $\bm{\hat{W}}^{shr}$ is a shrinkage estimator more suited to large dimensions proposed by \citet{Schafer2005}.  Also $\tau = \frac{\sum_{i \ne j}\hat{\text{Var}}(\hat{w}_{ij})}{\sum_{i \ne j}{\hat{w}}^2_{ij}}$ where $w_{ij}$ are elements of $\hat{\bm W}^{sam}$.}\label{table:2}
	\centering\setstretch{1.5}
	\begin{tabular}{lll}
		\toprule
		\textbf{Method} & \textbf{$\bm{W}$} & \textbf{ $\bm{R}'_\bot$}      \\
		\midrule
		OLS             &
		$\bm{I}$  &
		$\bm{S}'$  \\
		MinT(Sample)    &
		$\bm{\hat{W}}^{sam}$ &
		$\bm{S}'(\bm{\hat{W}}^{sam})^{-1}$ \\
		MinT(Shrink)    &
		$\tau\text{Diag}(\bm{\hat{W}}^{sam}) + (1-\tau)\bm{\hat{W}}^{sam}$ &
		$\bm{S}'(\bm{\hat{W}}^{shr})^{-1}$ \\
		WLS       &
		$\text{Diag}(\bm{\hat{W}}^{shr})$ &
		$\bm{S}'(\bm{\hat{W}}^{wls})^{-1}$ \\
		\bottomrule
	\end{tabular}
\end{table}

@@

Point reconciliation methods based on projections will always minimise the distance between unreconciled and reconciled forecasts, however the specific distance will depend on the choice of ${\bm R}$.  For example OLS minimises the Euclidean distance between $\hat{\bm y}$ and $\tilde{\bm y}$. \cite{Wickramasuriya2017} while MinT
minimises the Mahalonobis distance between $\hat{\bm y}$ and $\tilde{\bm y}$.  Bottom up methods minimise distance between reconciled and unreconciled forecasts only along dimensions corresponding to the bottom level series.  As such, bottom up methods should be thought of as a boundary case of reconciliation methods, since they ultimately do not use information at all levels of the hierarchy.

@@

\begin{theo}[Distance reducing property]
	If $\tilde{\bm y}_{t+h|t}={\bm S}{\bm G}\hat{\bm y}_{t+h|t}$ where ${\bm G}$ is such that ${\bm S}{\bm G}$ is an orthogonal projection then the following inequality holds
	  \begin{equation}
	    ||(\tilde{\bm y}_{t+h|t}-{\bm y}_{t+h})||^2_2\le||(\hat{\bm y}_{t+h|t}-{\bm y}_{t+h})||^2_2
	  \end{equation}
\end{theo}
\begin{proof}
	Since the aggregation constraints must hold for all realisations, ${\bm y}_{t+h}\in\frak{s}$ and ${\bm y}_{t+h}={\bm S}{\bm G}{\bm y}_{t+h}$ whenever ${\bm S}{\bm G}$ is a projection.  Therefore 
	\begin{align}
	||(\tilde{\bm y}_{t+h|t}-{\bm y}_{t+h})||_2&=||({\bm S}{\bm G}\hat{\bm y}_{t+h|t}-{\bm S}{\bm G}{\bm y}_{t+h})||_2\\
	&=||{\bm S}{\bm G}(\hat{\bm y}_{t+h|t}-{\bm y}_{t+h})||_2\\
	\end{align}
	The Cauchy-Schwarz inequality can be used to show that orthogonal projections are bounded operators\todo{Find reference or prove}, therefore
	 \begin{equation*}
	 ||{\bm S}{\bm G}(\hat{\bm y}_{t+h|t}-{\bm y}_{t+h})||_2\le
	 ||(\hat{\bm y}_{t+h|t}-{\bm y}_{t+h})||_2
	 \end{equation*}
\end{proof}
The inequality is strict whenever $\hat{\bm y}_{t+h|t}\notin\mathfrak{s}$.

@@

The log score can be approximated using a sample of values from the probabilistic forecast density \citep{Jordan2017} however it is more commonly used when a parametric form for the density is available for the probabilistic forecast.  The energy score on the other hand can be defined in terms of the characteristic function of the probabilistic forecast, but the representation in terms of expectations leads itself to easy computation when samples from the probabilistic forecast are available. 
An interesting limiting case is where $\alpha=2$, where it can be easily shown that
\begin{equation} \label{eq:(5.1)}
\text{ES}(\breve{\bm{Y}_{T+h},y_{T+h}}) = \|\bm{y}_{T+h}-\breve{\bm{\mu}}_{T+h}\|^2,
\end{equation}
where $\breve{\bm{\mu}}_{T+h} =\E_{\bm{F}}(\breve{\bm{Y}}_{T+h}) $. In this limiting case, the energy score only measures the accuracy of the forecast mean, and not the entire distribution and the energy score is proper, but not strictly proper. \citet{Pinson2013a} also argues that the energy score has very low discriminative ability for incorrectly specified covariances, even though it discriminates the misspecified means well.

@@

A similar issue also arises when discrete random variables are modelled as if they were continuous, an issue discussed in Section 4.1 of \cite{Gneiting2007}. This implies that the log score should be avoided when comparing reconciled and unreconciled probabilistic forecasts.

>>>>

%\theoremstyle{theo}
\newtheorem{theo}{Theorem}[section]

@@

\begin{abstract}
  Forecast reconciliation involves adjusting forecasts to ensure coherence with aggregation constraints. We extend this concept from point forecasts to probabilistic forecasts by redefining forecast reconciliation in terms of linear mappings in general, and projections more specifically. New theorems establish that the true predictive distribution can be recovered in the elliptical case by a linear mapping, and general conditions are derived for when this linear mapping is a projection. A geometric interpretation is also used to prove two new theoretical results for point forecasting; that reconciliation via projection both preserves unbiasedness and dominates unreconciled forecasts in a mean squared error sense. Strategies for forecast evaluation based on scoring rules are discussed, and it is shown that the popular log score is an improper scoring rule with respect to the class of unreconciled forecasts when the true predictive distribution coheres with aggregation constraints. Finally, evidence from a simulation study shows that reconciliation based on an oblique projection, derived from the MinT method of \citet{Wickramasuriya2017} for point forecasting, outperforms both reconciled and unreconciled alternatives.
\end{abstract}

\section{Introduction}\label{sec:intro}

%Sketch narrative to tell
%\begin{itemize}
%	\item Coherence is important in point forecasting to
%	\begin{itemize}
%		\item Align decisions
%		\item Improve forecasts
%	\end{itemize}
%	\item We propose a geometric interpretation via linear transformations including special case of projections.
%	\item These nest existing methods but the interpretation has advantages
%	\begin{itemize}
%		\item Prove that projections preserve unbiasedness. Previously assumed in special cases.
%		\item Prove reconciliation (using projection) always improves sum of squared errors (or a scaled/transformed version thereof).
%		\item Most importantly generalises to probabilistic forecasting.
%	\end{itemize}
%    \item For elliptical distributions, true predictive can be recovered via linear reconciliation and in special cases, via projection.
%    \item Discuss evaluation of forecasts
%    \begin{itemize}
%    	\item Log score improper when coherent v incoherent
%    	\item Energy score cn be used instead
%    	\item Discuss scores for coherent v coherent.
%    \end{itemize}
%    \item Finally evidence MinT is best from simulation
%\end{itemize}

Large collections of time series often follow some aggregation structure. For example, the electricity demand of a country can be disaggregated according to a geographic hierarchy of states, cities, and individual households, or by a temporal hierarchy of yearly, quarterly and monthly demand. In these so-called hierarchical time series, forecasts are often required for all individual series. To ensure aligned decision making, it is important for forecasts at the most disaggregated level add up to forecasts at more aggregated levels. This property is called ``coherence''. This issue has been extensively covered for point forecasting in a literature we review below, while the case of probabilistic forecasting is a gap that we seek to address in this work.

Traditional approaches to ensure coherent point forecasts produce first-stage forecasts at a single level of the hierarchy. To describe these we use the small hierarchy in Figure~\ref{fig1} where the variable labelled $Tot$ is the sum of the series $A$ and series $B$, the series $A$ is the sum of series $AA$ and series $AB$ and the series $B$ is the sum of the series $BA$ and $BB$. In the bottom-up approach \citep{Dunn1976}, forecasts are produced at the most disaggregated level (Series $AA$, $AB$, $BA$ and $BB$) and then summed to recover all higher-level series. Alternatively, in the top-down approach \citep{Gross1990}, a top-level forecast is first produced (Series $Tot$) and bottom level forecasts are recovered by disaggregating the forecast using either historical or forecasted proportions. A middle-out approach is a hybrid between these two, that for the hierarchy below would produce first stage forecasts for Series $A$ and $B$.

@@

In recent years, reconciliation methods introduced by \citet{Hyndman2011} have become increasingly popular. For these methods, first stage forecasts are independently produced for all series rather than series at a single level. Since these so-called `base' forecasts are rarely coherent in practice, they are subsequently adjusted or `reconciled' to ensure coherence. To date, reconciliation has typically been formulated as a regression problem with alternative reconciliation methods resembling different least squares estimators. These include Ordinary Least Squares {OLS} \citep{Hyndman2011}, Weighted Least Squares {WLS} \citep{AthEtAl2017}, and a Generalised Least Squares (GLS) estimator \citep{Wickramasuriya2017} named MinT since it minimises the trace of the squared error matrix. These methods have been shown to outperform traditional alternatives across a range of simulated and real-world datasets \citep{Hyndman2011,VanErven2015a,Wickramasuriya2017} since they use information at all levels of the hierarchy and, in some sense, hedge against the risk of model misspecification at a single level.

A shortcoming of the existing literature is a focus on point forecasting despite an increased understanding over the past decade of the importance of providing a full predictive distribution for forecast uncertainty \citep[see][and references therein]{Gneiting2014}. Indeed to the best of our knowledge, the (as yet unpublished) work of \citep{BenTaieb2017} is the only paper to deal with the issue of coherent probabilistic forecasts, and although they reconcile the means of the predictive distributions, the overall distributions are constructed in a bottom-up fashion rather than use a reconciliation process. In contrast, the main objective of our paper is to generalise both coherence and reconciliation from point to probabilistic forecasting.

To facilitate the extension of point forecast reconciliation to probabilistic forecasting, we first provide a geometric interpretation of existing point reconciliation methods, framing them in terms of projections. In addition to being highly intuitive, this allows us to establish a number of theoretical results. We prove two new theorems about point forecast reconciliation, the first showing that reconciliation via projections preserves the unbiasedness of base forecasts, while the second shows that reconciled forecasts dominate unreconciled forecasts since projections are bounded operators. We provide definitions of coherence and forecast reconciliation in the probabilistic setting, and describe how these definitions lead to a reconciliation procedure that merely involves a change of basis and marginalisation. We show that probabilistic reconciliation via linear transformations can recover the true predictive distribution as long as the latter is in the elliptical class. We provide conditions for which this linear transformation is a projection, and although this projection cannot be feasibly estimated in practice, we provide a heuristic argument in favour of MinT reconciliation.

We also cover the issue of forecast evaluation of probabilistic forecasts via scoring rules. In particular, we prove that for a coherent data generating process, the log score is not proper with respect to incoherent forecasts. As such we recommend the use of the energy score or variogram score for comparing reconciled to unreconciled forecasts. Two or more reconciled forecasts can be compared using log score, energy score or variogram score, although we show that comparisons should be made on the full hierarchy for the latter two scores.

The remainder of the papers is structured as follows. In Section~\ref{sec:definitions} coherence is defined geometrically for both point and probabilistic forecasts. Section~\ref{sec:reconciliation} contains definitions of point and probabilistic forecast reconciliation as well as our main theoretical results. In Section~\ref{sec:evaluation} we consider the evaluation of probabilistic hierarchical forecasts via scoring rules, while a simulation study comparing unreconciled probabilistic forecasts and different kinds of reconciled probabilistic forecasts is provided in Section~\ref{sec:gaussian}. Section~\ref{sec:conclusions} concludes with some discussion and thoughts on future research.

@@

%As an alternative to these traditional methods, \citet{Hyndman2011} proposed to utilize the information from all levels of the hierarchy to obtain coherent point forecasts in a two stage process. In the first stage, the forecasts of all series are independently obtained by fitting univariate models for individual series in the hierarchy. It is unlikely that these forecasts are coherent. Thus in the second stage, these forecasts are optimally combined through a regression model to obtain coherent forecasts. This second step is referred to as ``reconciliation'' since it takes a set of incoherent forecasts and revises them to be coherent. The approach was further improved by \citet{Wickramasuriya2017} who proposed the ``MinT'' algorithm to obtain optimally reconciled point forecasts by minimizing the mean squared coherent forecast errors.

@@

%\section{Hierarchical Time Series}\label{sec:notation}

\section{Coherent forecasts}\label{sec:definitions}

\subsection{Notation and Preliminaries}\label{sec:notation}

Throughout the paper, we will follow notational conventions used in \citet{Wickramasuriya2017} as much as possible. A {\em hierarchical time series} is a collection of $n$ variables where some variables are aggregates of other variables and we let $\bm{y}_t \in \mathbb{R}^n$ be a vector comprised of observations of all variables in the hierarchy at time $t$. For example for the hierarchy in Figure~\ref{fig1}, $n=7$ and $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$. The {\em bottom level series} are defined as those $m$ variables that cannot be formed as aggregates of other variables, we let $\bm{b}_t \in \mathbb{R}^m$ be a vector comprised of observations of all bottom-level series at time $t$. For example for the hierarchy in Figure~\ref{fig1}, $m=4$ and $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$. The hierarchical structure of the data imply the following holds for all $t$:
\begin{equation}
  \bm{y}_t = \bm{Sb}_t,
\end{equation}
where $\bm{S}$ is an $n \times m$ constant matrix that encodes the aggregation constraints. For the hierarchy in Figure~\ref{fig1}
$$
  \bm{S} = \begin{pmatrix}
               1& 1 &1 &1  \\
               1 &1 & 0 &0 \\
               0&0  & 1 & 1 \\
               & \multicolumn{2}{c}{\bm{I}_4} &
           \end{pmatrix},
$$
where $\bm{I}_4$ is a $4\times 4$ identity matrix.

@@

Let $\hat{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be any set of incoherent point forecasts at time $t+h$ using information up to and including time $t$. Let $\bm{G}$ and $\bm{d}$ be an $m\times n$ matrix and $m\times 1$ vector respectively and $g:\mathbb{R}^n \rightarrow \mathbb{R}^m$ be the mapping $g(\bm{y})={\bm G}{\bm y}+{\bm d}$.
\begin{definition}\label{def:reconpoint}
  The point forecast $\tilde{\bm{y}}_{t+h|t}$ ``reconciles'' $\hat{\bm{y}}_{t+h|t}$ with respect to the mapping $g(.)$ iff
  \begin{equation}
    \tilde{\bm{y}}_{t+h|t}=\bm{S}\left(\bm{G}\hat{\bm{y}}_{t+h|t}+{\bm d}\right)\,.
  \end{equation}
\end{definition}

@@

\begin{table}[!h]
	\caption{Summary of reconciliation methods that are projections. Here, $\bm{\hat{W}}^{sam}$ is the variance covariance matrix of one-step ahead forecast errors, while $\bm{\hat{W}}^{shr}$ is a shrinkage estimator more suited to large dimensions proposed by \citet{Schafer2005}. Also $\tau = \frac{\sum_{i \neq j}\hat{\text{Var}}(\hat{w}_{ij})}{\sum_{i \neq j}{\hat{w}}^2_{ij}}$ where $w_{ij}$ are elements of $\hat{\bm W}^{sam}$.}\label{table:2}
	\centering\setstretch{1.5}
	\begin{tabular}{lll}
		\toprule
		\textbf{Method} & \textbf{$\bm{W}$} & \textbf{ $\bm{R}'_\bot$}      \\
		\midrule
		OLS             &
		$\bm{I}$  &
		$\bm{S}'$  \\
		MinT(Sample)    &
		$\bm{\hat{W}}^{sam}$ &
		$\bm{S}'(\bm{\hat{W}}^{sam})^{-1}$ \\
		MinT(Shrink)    &
		$\tau\text{Diag}(\bm{\hat{W}}^{sam}) + (1-\tau)\bm{\hat{W}}^{sam}$ &
		$\bm{S}'(\bm{\hat{W}}^{shr})^{-1}$ \\
		WLS       &
		$\text{Diag}(\bm{\hat{W}}^{shr})$ &
		$\bm{S}'(\bm{\hat{W}}^{wls})^{-1}$ \\
		\bottomrule
	\end{tabular}
\end{table}

@@

Point reconciliation methods based on projections will always minimise the distance between unreconciled and reconciled forecasts, however the specific distance will depend on the choice of ${\bm R}$. For example OLS minimises the Euclidean distance between $\hat{\bm y}$ and $\tilde{\bm y}$. \citet{Wickramasuriya2017} while MinT
minimises the Mahalonobis distance between $\hat{\bm y}$ and $\tilde{\bm y}$. Bottom up methods minimise distance between reconciled and unreconciled forecasts only along dimensions corresponding to the bottom level series. As such, bottom up methods should be thought of as a boundary case of reconciliation methods, since they ultimately do not use information at all levels of the hierarchy.

@@

\begin{theo}[Distance reducing property]
	If $\tilde{\bm y}_{t+h|t}={\bm S}{\bm G}\hat{\bm y}_{t+h|t}$ where ${\bm G}$ is such that ${\bm S}{\bm G}$ is an orthogonal projection then the following inequality holds
	  \begin{equation}
	    ||(\tilde{\bm y}_{t+h|t}-{\bm y}_{t+h})||^2_2\le||(\hat{\bm y}_{t+h|t}-{\bm y}_{t+h})||^2_2
	  \end{equation}
\end{theo}
\begin{proof}
	Since the aggregation constraints must hold for all realisations, ${\bm y}_{t+h}\in\mathfrak{s}$ and ${\bm y}_{t+h}={\bm S}{\bm G}{\bm y}_{t+h}$ whenever ${\bm S}{\bm G}$ is a projection. Therefore
	\begin{align}
	||(\tilde{\bm y}_{t+h|t}-{\bm y}_{t+h})||_2&=||({\bm S}{\bm G}\hat{\bm y}_{t+h|t}-{\bm S}{\bm G}{\bm y}_{t+h})||_2\\
	&=||{\bm S}{\bm G}(\hat{\bm y}_{t+h|t}-{\bm y}_{t+h})||_2\\
	\end{align}
	The Cauchy-Schwarz inequality can be used to show that orthogonal projections are bounded operators\todo{Find reference or prove}, therefore
	 \begin{equation*}
	 ||{\bm S}{\bm G}(\hat{\bm y}_{t+h|t}-{\bm y}_{t+h})||_2\le
	 ||(\hat{\bm y}_{t+h|t}-{\bm y}_{t+h})||_2
	 \end{equation*}
\end{proof}
The inequality is strict whenever $\hat{\bm y}_{t+h|t}\notin\mathfrak{s}$.

@@

The log score can be approximated using a sample of values from the probabilistic forecast density \citep{Jordan2017} however it is more commonly used when a parametric form for the density is available for the probabilistic forecast. The energy score on the other hand can be defined in terms of the characteristic function of the probabilistic forecast, but the representation in terms of expectations leads itself to easy computation when samples from the probabilistic forecast are available.
An interesting limiting case is where $\alpha=2$, where it can be easily shown that
\begin{equation} \label{eq:(5.1)}
\text{ES}(\breve{\bm{Y}_{T+h},y_{T+h}}) = \|\bm{y}_{T+h}-\breve{\bm{\mu}}_{T+h}\|^2,
\end{equation}
where $\breve{\bm{\mu}}_{T+h} =\E_{\bm{F}}(\breve{\bm{Y}}_{T+h}) $. In this limiting case, the energy score only measures the accuracy of the forecast mean, and not the entire distribution and the energy score is proper, but not strictly proper. \citet{Pinson2013a} also argues that the energy score has low discriminative ability for incorrectly specified covariances, even though it discriminates the misspecified means well.

@@

A similar issue also arises when discrete random variables are modelled as if they were continuous, an issue discussed in Section 4.1 of \citet{Gneiting2007}. This implies that the log score should be avoided when comparing reconciled and unreconciled probabilistic forecasts.
